---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# simulationRNG

<!-- badges: start -->
<!-- badges: end -->

The goal of simulationRNG is to provide a package to generate psuedo-random number and random variates while given the user access to the source code for verification, modification, and improvement. 


## Installation

This package was developed using R version 4.1, although no functions should have version dependencies, it does seem to require at least this version for installation of the package. You can install the latest released version of simulationRNG using Rstudio with the following command:


devtools::install_github("donovanquimby/simulationRNG")


The package can also be directly downloaded or cloned from from https://github.com/donovanquimby/simulationRNG.


## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(simulationRNG)

# uniform(0,1) distriubtion
u <- unif(n = 1e5, type = "bfs1987")
hist(u)

# Gamma Distribution
g <- gammaSim(n=5e2, shape =2, scale = 2)
hist(g)

# Multivariate Normal Distribution
cov_matrix = matrix(c(1,0.9,0.9,1), nrow = 2, ncol = 2)
mn <- multiNormal(n=7e2, cov_matrix = cov_matrix,  mu=c(0,0), seed = 122)
plot(mn)
```




