---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# simulationRNG

<!-- badges: start -->
<!-- badges: end -->

The goal of simulationRNG is to provide a package to generate psuedo-random number and random variates while given the user access to the source code for verification, modification, and improvement. 


## Installation

You can install the released version of simulationRNG from [github](https://github.gatech.edu/dquimby3/simulationRNG.git) with:

``` r
devtools::install_github("dquimby3/simulationRNG")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(simulationRNG)

# uniform(0,1) distriubtion
u <- unif(n = 1e5, type = "bfs1987")
hist(u)

# Gamma Distribution
g <- gammaSim(n=5e2, shape =2, scale = 2)
hist(g)

# Multivariate Normal Distribution
cov_matrix = matrix(c(1,0.9,0.9,1), nrow = 2, ncol = 2)
mn <- multiNormal(n=7e2, cov_matrix = cov_matrix,  mu=c(0,0), seed = 122)
plot(mn)
```




